Local PCA results

### 2018-05-14 templated/summarize_run.Rmd
config missing error msg

```{r data_setup, include=FALSE}
opt <- fromJSON("config.json")
if (is.null(opt$weights)) { opt$weights <- 1 }

>>>>

```{r data_setup, include=FALSE}
if (!file.exists("config.json")) {
    stop(paste("File", file.path(getwd(), "config.json"), "does not exist. Cannot continue."))
}
opt <- fromJSON("config.json")
if (is.null(opt$weights)) { opt$weights <- 1 }
